\bf On semidefinite-representable sets over valuation fields

### 2025-05-15 article/paper_padic_spec.tex
package algo
commit by Simone

\documentclass[a4paper,12pt]{article}

@@

\usepackage{geometry}
\geometry{
 a4paper,
 %total={170mm,257mm},
 left=35mm,
 top=40mm,
 bottom=20mm
}

@@

@@

\textheight235mm
\textwidth165mm
\voffset-10mm
\hoffset-12.5mm
\parindent0.8cm
\parskip0mm

>>>>

\documentclass[a4paper,oneside,11pt]{article}

@@

@@

% --------- ALGORITHMS ---------- <<:
\usepackage[noend]{algpseudocode}      %%% this is for the algorithms
\renewcommand{\algorithmicrequire}{\textbf{Input:}} % require --> input
\renewcommand{\algorithmicensure}{\textbf{Output:}} % ensure --> output
\algrenewcomment[1]{\hfill \(\triangleright\) \emph{\small #1}} % to italicize text in comments
\algnewcommand{\CommentLine}[1]{\(\triangleright\) \emph{\small #1}} % whole line comment
\algnewcommand{\InlineIf}[2]{ % single line if-then
  \State \algorithmicif\ #1\ \algorithmicthen\ #2}
\algnewcommand{\InlineIfElse}[3]{ % single line if-then-else
  \State \algorithmicif\ #1\ \algorithmicthen\ #2\ \algorithmicelse\ #3}
\algnewcommand{\InlineFor}[2]{\algorithmicfor\ #1\ \algorithmicdo\ #2} % single line for loop
%% Change call to put a clickable link, and ensure no parentheses if
%% no argument is given
%% Original command from package for reference:
%% \algnewcommand\Call[2]{\textproc{#1}\ifthenelse{\equal{#2}{}}{}{(#2)}}
\algrenewcommand\Call[2]{\nameref{#1}\ifthenelse{\equal{#2}{}}{}{\ensuremath{(#2)}}}%
\newcommand{\algoName}[1]{Algorithm \nameref{#1}}
%% make sure the arguments of the algorithm are not stored in nameref
\makeatletter
\newcommand{\algoCaptionLabel}[2]{%
     \NR@gettitle{\textproc{#1}}% % NR@gettitle to have nameref work fine with algos
     \caption[\textproc{#1}]{\textproc{#1}\ifthenelse{\equal{#2}{}}{}{$(#2)$}}%
     \label{algo:#1}
     }%
\makeatother
%% to fix references to algo lines (problem is because of load order in siamonline cls)
\makeatletter
  \g@addto@macro\ALG@step{%
    \addtocounter{ALG@line}{-1}%
    \refstepcounter{ALG@line}%
    \expandafter\@cref@getprefix\cref@currentlabel\@nil\cref@currentprefix%
    \xdef\cref@currentprefix{\cref@currentprefix}}%
  \g@addto@macro\ALG@beginalgorithmic{%
    \def\cref@currentlabel{%
      [line][\arabic{ALG@line}][\cref@currentprefix]\theALG@line}}%
\makeatother
%% to be able to use statex with some indentation, typically in an if statement
%% from https://tex.stackexchange.com/questions/33979/include-a-line-break-in-algorithmic-while-maintaining-indentation/33995#33995
\makeatletter
\newcommand{\StateX}[1]{%
  \setlength\@tempdima{\algorithmicindent}%
  \Statex\hskip\dimexpr#1\@tempdima\relax}
\makeatother
% :>> ALGORITHMS

@@

\usepackage{geometry}
\geometry{
 a4paper,
 %total={170mm,257mm},
 left=30mm,
 right=30mm,
 top=30mm,
 bottom=30mm
}

%\textheight235mm
%\textwidth165mm
%\voffset-10mm
%\hoffset-12.5mm
\parindent0.8cm
\parskip0mm
